### 2021-05-10 papers/SYRCoSE/intro.tex
minor

Our goal is to develop a \coq library containing 
a comprehensive set of common definitions, lemmas, 
and tactics that would allow researchers 
to utilise the theory of event structures 
for the needs of their domain.

>>>>

Our end goal is to develop a \coq library containing 
a comprehensive set of common definitions, lemmas, 
and tactics that would allow researchers 
to utilise the theory of event structures 
for the needs of their domain.
